---
title: "CatDrought"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CatDrought}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lfcdata)
library(dplyr)
```

## CatDrought database

CatDrought database offers access to drought stress, soil water content and other
modeled variables for Catalunya.

```{r catdroughtdb}
catdroughtdb <- catdrought()
catdroughtdb
```


## Access to the data

CatDrought offers precalculated data at 1km resolution as rasters. This spatial
data can be accesed with the `catdrought_get_raster` function:

### Raster formats

This function allows to access the raster for a specified date (as character),
and returns a spatial object, whose class depends on the spatial argument.
Available classes are `raster` (a *RasterBrick* object) and `stars`
(a *stars* object).

```{r get_raster_stars}
catdrought_get_raster(
  catdroughtdb,
  date = as.character(Sys.Date() - 1),
  spatial = 'stars'
)
```

```{r get_raster_raster}
catdrought_get_raster(
  catdroughtdb,
  date = as.character(Sys.Date() - 1),
  spatial = 'raster'
)
```

  - `date`: a character indicating the date to extract
  - `spatial`: a character indicating the output class (`raster` or `stars`)


### Dates available

Only a natural year (365 days from the day before current date) are available

```{r get_raster_dates}
catdrought_get_raster(
  catdroughtdb,
  date = as.character(Sys.Date() - 365),
  spatial = 'stars'
)
```

## Time series data for spatial points or polygons

Instead of rasters, we can obtain a table with the time series for a specified
variable. This time series covers all the available dates. For this, we can
use the `catdrought_get_current_time_series` function.

### Points

This will extract the values for the desired variable on all the dates available,
for the set of points provided:

```{r time_series_points}
# points spatial object, obtained from fes database
points_sf <- lfcdata::fes()$get_data('plot_nfi_4_results', spatial = TRUE) %>%
  slice(1:5)

catdrought_get_current_time_series(
  catdroughtdb,
  sf = points_sf,
  variable = 'Eplant'
)
```


  > NOTE: This can take some time depending on the resolution and the
  number of features.

  - `sf` object with the POINT features
  - `variable` the desired variable

### Polygons

The process is exactly the same as for points:

```{r time_series_polygons}
# points spatial object, obtained from fes database
polygons_sf <- lfcdata::lidar()$get_data('lidar_municipalities', 'AB') %>%
  slice(1:5)

catdrought_get_current_time_series(
  catdroughtdb,
  sf = polygons_sf,
  variable = 'Eplant'
)
```


Here an average with standard error values are returned for all polygons and
dates.

> NOTE: This can take some time depending on the resolution and the
  number of features.

  - `sf` object with the POLYGON or MULTIPOLYGON features
  - `variable` the desired variable

